ODGI: understanding pangenome graphs

### 2021-10-21 manuscript/fig_odgi_viz.tex
C4 locus scripting

\begin{figure*}[h!]
	\begin{subfigure}{\linewidth}
		\caption{}
		\centering
		% include first image
		\includegraphics[width=1.0\linewidth]{fig/metrics/chr4_pan_HTTex1_gfa_multiqc_odgi_stats.png}  
		\label{fig:metrics-multiqc}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\caption{}
		\centering
		% include second image
		\includegraphics[width=1.0\linewidth, trim=0 0 -1cm 0 ]{fig/metrics/chr4_pan_fa_a2fb268_e820cd3_9ea71d8_smooth_gfa_og_HTTex1_og_O_og_tiny_og_png_svg.pdf}  
		\label{fig:metrics-viz}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\caption{}
		\centering
		% include second image
		\includegraphics[width=\linewidth,trim=+.225cm 0 +0.425cm +2cm]{fig/metrics/chr4_HTT_chm13_depth_w1_bed.pdf}  
		\label{fig:metrics-depth}
	\end{subfigure}
	\begin{subfigure}{1\linewidth}
		\caption{}
		\centering
		% include fourth image
		\includegraphics[width=\linewidth,trim=+.225cm 0 +.425cm +2cm]{fig/metrics/chr4_HTT_chm13_degree_w1_bed.pdf}  
		\label{fig:metrics-degree}
	\end{subfigure}
%	\includegraphics[width=\linewidth]{fig/metrics/chr4.pan.HTTex1.gfa.multiqc_odgi_stats.png}
	\caption{Visualizing the (\textit{C4 locus}) from a human pangenome graph of 90 haplotypes: \textbf{(a)} standard mode: explain the bio stuff. \textbf{(b)} odgi viz's color by path position: explain the bio stuff XXX. \textbf{(c)} odgi viz's color by strandness: explain the bio stuff XXX. `textbf{(d)}  odgi viz's color by coverage: explain the bio stuff XXX.}
	\label{fig:odgi_viz}
\end{figure*}

>>>>

\begin{figure*}[h!]
    \begin{subfigure}{\linewidth}
        \caption{}
        \centering
        % include first image
        \includegraphics[width=1.0\linewidth, trim=0 +2cm 0 0]{fig/visualization_1D/chr6.pan.fa.a2fb268.e820cd3.9ea71d8.smooth.gfa.og.grch38_chr6_31889244-32095493.0.sorted}
        \label{fig:odgi_viz_default}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
        \caption{}
        \centering
        % include second image
        \includegraphics[width=1.0\linewidth, trim=0 +2cm 0 0]{fig/visualization_1D/chr6.pan.fa.a2fb268.e820cd3.9ea71d8.smooth.gfa.og.grch38_chr6_31889244-32095493.0.sorted.du}
        \label{fig:odgi_viz_color_by_path_pos}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
        \caption{}
        \centering
        % include second image
        \includegraphics[width=\linewidth, trim=0 +2cm 0 0]{fig/visualization_1D/chr6.pan.fa.a2fb268.e820cd3.9ea71d8.smooth.gfa.og.grch38_chr6_31889244-32095493.0.sorted.z}
        \label{fig:odgi_viz_color_by_inversion_rate}
    \end{subfigure}
    \begin{subfigure}{1\linewidth}
        \caption{}
        \centering
        % include fourth image
        \includegraphics[width=\linewidth, trim=0 0 0 0]{fig/visualization_1D/chr6.pan.fa.a2fb268.e820cd3.9ea71d8.smooth.gfa.og.grch38_chr6_31889244-32095493.0.sorted.m}
        \label{fig:odgi_viz_color_by_path_depth}
    \end{subfigure}
    \caption{Visualizing the complement component 4 (C4) \textit{locus} from a human pangenome graph of 90 haplotypes: \textbf{(a)} standard mode: explain the bio stuff. \textbf{(b)} odgi viz's color by path position: explain the bio stuff XXX. \textbf{(c)} odgi viz's color by strandness: explain the bio stuff XXX. `textbf{(d)}  odgi viz's color by coverage: explain the bio stuff XXX.}
    \label{fig:odgi_viz}
\end{figure*}

### 2021-10-21 manuscript/main.tex
C4 locus scripting

% pjotr & andrea
ODGI maintains its own efficient binary format for storing graphs on disk.
ODGI also supports reading and writing the textual GFA file format for interchange with other tools such as with the VG toolkit toolkit~\citep{Garrison:2018}.

@@

However, complex, nonlinear graph structures are difficult to display and interpret in a convenient low number of dimensions.
To overcome such a limitation, \textit{odgi viz} supports multiple visualization modes (Fig. \ref{fig:odgi_viz}\textbf{b-d}), making it easy to grasp the properties of the graph and its complexity.
% Explain here 3 odgi viz modes

>>>>

% pjotr & andrea
ODGI maintains its own efficient binary format for storing graphs on disk.
ODGI also supports reading and writing the textual GFA file format for interchange with other tools such as with the VG toolkit~\citep{Garrison:2018}.

@@

Nevertheless, complex, nonlinear graph structures are difficult to display and interpret in a convenient low number of dimensions.
To overcome such a limitation, \textit{odgi viz} supports multiple visualization modes (Fig. \ref{fig:odgi_viz}\textbf{b-d}), making it easy to grasp the properties of the graph and its complexity.
% Explain here 3 odgi viz modes
